\documentclass{article}

\usepackage[final]{neurips_2019}

\usepackage{xeCJK}
\setCJKmainfont{Noto Sans CJK TC}

\usepackage[
    colorlinks=true,
    urlcolor=blue,
]{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{lipsum}


\newcommand{\note}[1]{\textcolor{blue}{{#1}}}

\title{
  NTU 2025 Fall Applied Deep Learning HW2 Report \\
  \vspace{1em}
  \small{\normalfont NTU CSIE 5431 Applied Deep Learning}
}

\author{
  CHIH-HAO LIAO \\
  {\hypersetup{urlcolor=black}\href{https://www.fo.ntu.edu.tw/}{School of Forestry and Resource Conservation}}\\
  {\hypersetup{urlcolor=black}\href{https://www.bebi.ntu.edu.tw/}{Graduate Institute of Biomedical Electronics and Bioinformatics}}\\
  {\hypersetup{urlcolor=black}\href{https://www.ntu.edu.tw/}{National Taiwan University}}\\
  {\hypersetup{urlcolor=black}\href{mailto:R11625015@ntu.edu.tw}{\texttt{R11625015@ntu.edu.tw}}} \\
}

\begin{document}

\maketitle

\section{Q1: LLM Tuning (10\%)}
\subsection{Describe: (6\%)}
\begin{itemize}
    \item How much training data did you use? (2\%)
    \item How did you tune your model? (2\%)
    \item What hyper-parameters did you use? (2\%)
\end{itemize}

\subsection{Show your performance: (4\%)}
\begin{itemize}
    \item What is the final performance of your model on the public testing set? (2\%)
    \item Plot the  learning curve on the public testing set (2\%)
\end{itemize}

\section{Q2: LLM Inference Strategies (5\%)}
\subsection{Zero-Shot (1\%)}
\begin{itemize}
    \item What is your setting? How did you design your prompt? (1\%)
\end{itemize}

\subsection{Few-Shot (In-context Learning) (2\%)}
\begin{itemize}
    \item What is your setting? How did you design your prompt? (1\%)
    \item How many in-context examples are utilized? How you select them? (1\%)
\end{itemize}

\subsection{Comparison: (1\%)}
\begin{itemize}
    \item What's the difference between the results of zero-shot, few-shot, and LoRA? (2\%)
\end{itemize}

\section{Q3: Bonus: Try Llama3-Taiwan (8B) (2\%)}
\begin{itemize}
    \item \href{https://huggingface.co/yentinglin/Llama-3.1-Taiwan-8B}{Llama-3-8b} trained by traditional Chinese data
    \item Tune this model on the classical chinese data
    \item Describe your experimental settings and compare the results to those obtained from your original methods
\end{itemize}

\end{document}
